Being able to feel sound has been a point of interest for many who cannot hear it. Appealing to those who cannot hear sound, this sound vest will be designed with the purpose to allow the body to feel the sound so clearly, it’s as if the body can now translate these feelings to how soundwaves would be interpreted in the brain. This application can be applied to many different uses. For example, if someone who is deaf wants to listen to music, there is now another option. They will now be able to feel the low frequencies where the bass lies, the mid frequencies where the voice and other instruments are located, and the high frequencies where the remaining frequencies are  located. Another application of this device is when a user is playing a video game. Inspired by how a gaming console controller can vibrate when doing something like shooting a gun, the vest will intake the sound being played and also vibrate along to what Is going on in the game. This gives the user an immersive experience to make the game feel and sound (for those who can hear) like they are in the game. Also, another application is when an individual is watching a movie in their living room or home theater. Once the vest is connected to the movies sound system, you will be able to vividly feel the richness of things like the sound of a bass guitar in an intro song to the deep rumbles a spaceship engine delivers while on screen. Movies will be brought to like with the sense of touch in mind. This product is ideally purposed to give those who are deaf another avenue to “hear” sound again. That is the vision of this vest. To deliver sound to the body, not just the ears.  
