This section provides a description of your product and defines it's primary features and functions. The purpose is to give the document reader/reviewer enough information about the product to allow them to easily follow the specification of requirements found in the remainder of the document. Your header for this section should introduce the section with a brief statement such as: "This section provides the reader with an overview of X. The primary operational aspects of the product, from the perspective of end users, maintainers and administrators, are defined here. The key features and functions found in the product, as well as critical user interactions and user interfaces are described in detail." Using words, and pictures or graphics where possible, specify the following:

\subsection{Features \& Functions}
What the product does and does not do. Specify in words what it looks like, referring to a conceptual diagram/graphic (Figure X).  Define the principle parts/components of the product. Specify the elements in the diagram/graphic that are part(s) of this product as well as any associated external elements (e.g., the Internet, an external web server, a GPS satellite, etc.)

\subsection{External Inputs \& Outputs}
\begin{table}[h]
\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Input/Output} & \textbf{Name} & \textbf{Description} & \textbf{Use} \\ \hline
 Input & Power Switch & simple 2-way switch & powering on system \\ \hline
 Input  & Volume/Intensity Knob & potentiometer & adjusting intensity of music \\ \hline
 Output  & Pre-Amp & audio amplifier & amplifying original signal source \\ \hline
 Output  & Filters & low, band, and high pass filters & filter signal  \\ \hline
 Output & Bass Shakers/Speakers & tactile transducers and vibrating motors & provide vibrating sensation to vest \\ \hline
\end{tabular}}
\end{table}

\subsection{Product Interfaces}
Specify what all operational (visible) interfaces look like to your end-user, administrator, maintainer, etc. Show sample/mocked-up screen shots, graphics of buttons, panels, etc. Refer to the critical external inputs and outputs described in the paragraph above.
